Ants-Review: A Protocol For Open Anonymous Peer-Reviews

### 2020-06-10 paper-v1.tex
cleanup by @naszam

From its birth in 2008 as a distributed ledger for the peer-to-peer electronic cash system Bitcoin \cite{BitcoinSatoshi}, blockchain technologies (BCTs) have spread far beyond the sole cryptocurrency domain, in particular after the implementation of a general purpose smart contract functionality introduced by Ethereum \cite{Ethereum}.

>>>>

From its birth in 2008 as a distributed ledger for the peer-to-peer electronic cash system Bitcoin \cite{Bitcoin}, blockchain technologies (BCTs) have spread far beyond the sole cryptocurrency domain, in particular after the implementation of a general purpose smart contract functionality introduced by Ethereum \cite{Ethereum}.
